r--- title: "R Notebook for Checking Normalization" output: html_notebook ---

# Define Variable

```{r Define Variable}
# run_table_path = 'run_table_complete.csv'
run_table_path = '../experiments/runner/experiments/new_runner_experiment/run_table.csv'
```

# Environment Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, results = 'hide')
```

# Install Packages

```{r Install Packages}
if (!require("ggplot2")) install.packages("ggplot2")
library(ggplot2)

if (!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

if (!require("dplyr")) install.packages("dplyr")
library(dplyr)

if (!require("bestNormalize")) install.packages("bestNormalize")
library(bestNormalize)

if (!require("xtable")) install.packages("xtable")
library(xtable)

if (!require("effsize")) install.packages("effsize")
library(effsize)
```

# Analysis

## Load data and transform relevant variable into factors

```{r setup}
cat("Loading Data:","\n")
energy_df <- read.csv(run_table_path)
energy_df$problem = as.factor(energy_df$problem)
energy_df$prompts = as.factor(energy_df$prompts)
energy_df$run_number <- gsub(".*_(\\d+)$", "\\1", energy_df$X__run_id)
energy_df$run_number = as.factor(energy_df$run_number)
str(energy_df)
energy_df <- energy_df %>%
  mutate(energy_consumption = energy_usage * execution_time)
human_base_df <- subset(energy_df, prompts %in% c("human", "base_prompt"))
str(human_base_df)
```

## Draw histogram

```{r, message=FALSE, warning=FALSE, results='hide'}
energy_df %>%
  group_by(problem, prompts) %>%
  group_split() %>%
  lapply(function(group_data) {
    hist(group_data$energy_consumption, 
         main = unique(group_data$problem), 
         xlab = "Energy consumption")
  })
```

```{r}
energy_df %>%
  group_by(problem, prompts) %>%
  summarize(n = n(),
            stest = shapiro.test(energy_consumption)$p.value)
```

## Mean Mode Std

```{r energy stats table}
# Create summary statistics with mean, variance, standard deviation, max, and min
summary_stats <- energy_df %>%
  group_by(problem, prompts) %>%
  summarise(
    
    energy_avg = mean(energy_consumption),
    energy_var = var(energy_consumption),
    energy_sd = sd(energy_consumption),
    energy_min = min(energy_consumption),
    energy_max = max(energy_consumption),
    
    .groups = 'drop'
  )

# Create and format the xtable
summary_table <- xtable(summary_stats,
                       caption = "Summary Statistics for Energy Consumption by problem and prompts",
                       digits = c(0, 0, 0, 2, 2, 2, 2, 2))

# Print the table (you can adjust the type of output as needed)
print(summary_table, 
      include.rownames = TRUE,
      floating = FALSE)

```

## Check Normalization

```{r, message=FALSE, warning=FALSE, results='hide'}

energy_df$norm_energy_consumption = bestNormalize(energy_df$energy_consumption)$x.t
energy_df %>%
  group_by(problem, prompts) %>%
  group_split() %>%
  lapply(function(group_data) {
    hist(group_data$norm_energy_consumption, 
         main = c(unique(group_data$problem), unique(group_data$prompts)), 
         xlab = "Energy consumption")
  })
```

```{r}
energy_df %>%
  group_by(problem, prompts) %>%
  summarize(n = n(),
            stest = shapiro.test(norm_energy_consumption)$p.value)
``` 
```{r check wilcos test}
wilcox_df <- energy_df %>%
  mutate(energy_consumption = energy_usage * execution_time)
wilcox_df$problem <- recode(wilcox_df$problem,
  "O_n_problem" = "O(n)",
  "O_nlog_problem" = "O(n log n)",
  "O_n2_problem" = "O(n^2)"
)

# Step 3: Filter to keep only the rows with prompts "human" or "base_prompt"
wilcox_df <- subset(wilcox_df, prompts %in% c("human", "base_prompt"))

# Step 4: Apply Mann-Whitney U Test for each problem
wilcox_results <- wilcox_df %>%
  group_by(problem) %>%
  summarise(
    p_value = wilcox.test(
      energy_consumption[prompts == "human"],
      energy_consumption[prompts == "base_prompt"]
    )$p.value
  )
print(wilcox_results)
```
```{r Effect Size Estimation with cliffs delta}

cliffs_delta_results <- wilcox_df %>%
  group_by(problem) %>%
  summarise(
    cliffs_delta = cliff.delta(
      energy_consumption[prompts == "human"],
      energy_consumption[prompts == "base_prompt"]
    )$estimate
  )

# Print the result
print(cliffs_delta_results)

```
```

```{r draw histogram based on mean value}
# Assuming 'energy_efficiency' is the column representing energy efficiency in your dataset
# Adjust the column name as needed

# Plot histograms comparing energy efficiency for each problem
mean_human_base_df <- human_base_df %>%
  group_by(problem, prompts) %>%
  summarise(mean_energy_consumption = mean(energy_consumption, na.rm = TRUE), .groups = 'drop')
#mean_human_base_df <- mean_human_base_df %>%
#  mutate(log_mean_energy_consumption = log(mean_energy_consumption))
mean_human_base_df <- mean_human_base_df %>%
  mutate(problem = recode(problem,
                          "O_n_problem" = "O(n)",
                          "O_nlogn_problem" = "O(nlogn)",
                          "O_n2_problem" = "O(n²)"))
mean_human_base_df$problem <- factor(mean_human_base_df$problem, levels = c("O(n)", "O(nlogn)", "O(n²)"))

str(mean_human_base_df)
ggplot(mean_human_base_df, aes(x = problem, y = mean_energy_consumption, fill = prompts)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.7) +
  geom_text(aes(label = round(mean_energy_consumption, 2)),
          position = position_dodge(width = 0.9), vjust = -0.5) +
  labs(title = "Mean Energy Efficiency by Problem",
       x = "Problem",
       y = "Mean Energy Efficiency") +
  scale_fill_manual(values = c("human" = "blue", "base_prompt" = "orange")) +
  theme_minimal()

```