# Overview
The Software Carbon Intensity (SCI) is a rate, carbon emissions per one unit of R. The equation used to calculate the SCI value of a software system is:

`SCI = ((E * I) + M) per R`

Where:

- E = Energy consumed by a software system
- I = Location-based marginal carbon emissions
- M = Embodied emissions of a software system
- R = Functional unit (e.g. carbon per additional user, API-call, ML job, etc) 

All the elements in the SCI equation scale by the same functional unit of “R”

# Definition

## (What) Software boundary
*Describe the components that are included in the software systems, if any major components are not included then please provide **reasons for exclusion**.*

### Included

All RunnerConfig experiment from python main programs

## (Scale) Functional Unit

*Describe the [functional unit](https://github.com/Green-Software-Foundation/software_carbon_intensity/blob/main/Software_Carbon_Intensity/Software_Carbon_Intensity_Specification.md#functional-unit-r) that best controls the scaling of the software system.*

The choice of functional unit applies to all components in your software boundary. 

R is one command of `python3 experiment-runner/ experiments/runner/RunnerConfig.py` over a 1 hour period

## (How) Quantification method

*For each software component in your software boundary, decide whether you are going to **measure** using real-world data or **calculate** an estimate via models, provide a reason and any useful details for each choice.
*


# Formulas

## Energy (`E`)
The Quantification method used for calculating energy value is **Calculate**. We are measuring CPU utilization of the app servers and then using a model based on the Thermal Design Power (TDP) of the processors, number of cores etc to **estimate** the power consumption.

The equation used to model the energy consumption is:

P[kwH] = (Power consumed by CPU or Pc Number of cores + Power consumed by Memory or Pr + Power consumed by GPU or Pg Number of GPUs)/1000

* We will use the energy usage and exection time from energibridge. First, we get energy consumption from sum(energy_usage * execution_time) and divide by sum(execution_time) * 1000 to get energy consumption per hour Then divide the result by 1000 to get the kwH
* E = (sum(energy_usage * execution_time) / sun(execution_time)) 1000 * 1000
* No GPU was used hence Pg ~0

### Carbon Intensity (`I`)

* We will use regional yearly averages.
* The region the application was run in was the Netherlands
* We will source the Carbon Intensity from [[I] Carbon intensity of electricity generation]https://ourworldindata.org/grapher/carbon-intensity-electricity?tab=chart&country=~NLD).


### Embodied Carbon (`M`)

The equation to calculate `M = TE * (TR/EL) * (RR/TR)`

Where:

* TE = Total Embodied Emissions, the sum of LCA emissions for all hardware components associated with the database server.
* TR = Time Reserved, the length of time the hardware is reserved for use by the software.
* EL = Expected Lifespan, the anticipated time that the equipment will be installed.
* RR = Resources Reserved, the number of resources reserved for use by the software.
* TR = Total Resources, the total number of resources available.

For this component:

* TE: The PC is Macbook Pro 16" (2019) with 394 kg CO2e. This data was sourced from the [CLaptop carbon footprints](https://github.com/rarecoil/laptop-co2e).
* TR: Sum of execution time.
* EL: We assume 1 year or 8766 hours
* RR: 12 vCPUs was used
* TR: 12 vCPUs was in the PC

# Execution

```{r calculate carbon intensity}
run_table_path = '../experiments/runner/experiments/new_runner_experiment/run_table.csv'

```

```{r Install Packages}
```

```{r setup}
cat("Loading Data:","\n")
data <- read.csv(run_table_path)
```

```{r energy}
# energy = average energy usage * 1 hour / 1000
# Calculate the energy consumption in kWh
data$energy_consumption <- (data$energy_usage * data$execution_time)
time <- sum(data$execution_time) / 1000
energy <- sum(data$energy_consumption) / time
# convert to hour
energy <- energy / 1000
# convert to kwH
energy <- energy / 1000
print(energy)
```
```{r}
# 268 grams of CO₂ equivalents per kilowatt-hour
carbon_intensity <- 268
```

```{r}
te <- 394
tir <- sum(data$execution_time) / 3600000
el <- 8766
rr <- 12
tor <- 12
m_carbon <- 394 * (tir / el) * (rr / tor)
print(tir)
print(m_carbon)
```
The result can be obtained as SCI = 12.07524
```{r}
sci <- (energy * carbon_intensity) + m_carbon
print(sci)
```