# Overview
The Software Carbon Intensity (SCI) is a rate, carbon emissions per one unit of R. The equation used to calculate the SCI value of a software system is:

`SCI = ((E * I) + M) per R`

Where:

- E = Energy consumed by a software system
- I = Location-based marginal carbon emissions
- M = Embodied emissions of a software system
- R = Functional unit (e.g. carbon per additional user, API-call, ML job, etc) 

All the elements in the SCI equation scale by the same functional unit of “R”

# Definition

## (What) Software boundary
*Describe the components that are included in the software systems, if any major components are not included then please provide **reasons for exclusion**.*

### Included

All RunnerConfig experiment from python main programs

## (Scale) Functional Unit

*Describe the [functional unit](https://github.com/Green-Software-Foundation/software_carbon_intensity/blob/main/Software_Carbon_Intensity/Software_Carbon_Intensity_Specification.md#functional-unit-r) that best controls the scaling of the software system.*

The choice of functional unit applies to all components in your software boundary. 

R is one command of `python3 experiment-runner/ experiments/runner/RunnerConfig.py` over a 1 hour period

## (How) Quantification method

*For each software component in your software boundary, decide whether you are going to **measure** using real-world data or **calculate** an estimate via models, provide a reason and any useful details for each choice.
*


# Formulas

## Energy (`E`)
The Quantification method used for calculating energy value is **Calculate**. We are measuring CPU utilization of the app servers and then using a model based on the Thermal Design Power (TDP) of the processors, number of cores etc to **estimate** the power consumption.

The equation used to model the energy consumption is:

P[kwH] = (Power consumed by CPU or Pc Number of cores + Power consumed by Memory or Pr + Power consumed by GPU or Pg Number of GPUs)/1000

* CPU Utilization doesn’t scale linearly with power consumption, we will use the power curve as described in the [SCI Data Project “[E] Energy Estimation from Utilization Model” model](https://docs.google.com/spreadsheets/d/1Viv94rMKH-fJrfD9Nn9_qkiAg1PDfIfJUAHRX9slG7A/edit#gid=526989613)
* TDP of server used in Azure App server Premium configuration (P2v2 ) -2nd Generation Intel® Xeon® Platinum 8272CL (Cascade Lake)= 205 W ( [https://ark.intel.com/content/www/us/en/ark/products/192482/intel-xeon-platinum-8270-processor-35-75m-cache-2-70-ghz.html](https://ark.intel.com/content/www/us/en/ark/products/192482/intel-xeon-platinum-8270-processor-35-75m-cache-2-70-ghz.html))
* From specs, we found that Power consumed by 4GB memory is close to 1.45 W and that by 8 GB memory is approximately 2.45 W. Also from this [article](https://medium.com/teads-engineering/estimating-aws-ec2-instances-power-consumption-c9745e347959) we can consider power consumed is approx 0.38 W/GB or close to 2.6 Watts.Since the energy values for memory are much lower than the calculated energy values for processors or CPUs, we consider these values negligible. Pr ~0
* No GPU was used hence Pg ~0

### Carbon Intensity (`I`)

* We will use regional yearly averages.
* The region the application was run in was the Netherlands
* We will source the Carbon Intensity from [[I] Carbon intensity of electricity generation]https://ourworldindata.org/grapher/carbon-intensity-electricity?tab=chart&country=~NLD).


### Embodied Carbon (`M`)

The equation to calculate `M = TE * (TR/EL) * (RR/TR)`

Where:

* TE = Total Embodied Emissions, the sum of LCA emissions for all hardware components associated with the database server.
* TR = Time Reserved, the length of time the hardware is reserved for use by the software.
* EL = Expected Lifespan, the anticipated time that the equipment will be installed.
* RR = Resources Reserved, the number of resources reserved for use by the software.
* TR = Total Resources, the total number of resources available.

For this component:

* TE: The PC is Macbook Pro 16" (2019) with 394 kg CO2e. This data was sourced from the [CLaptop carbon footprints](https://github.com/rarecoil/laptop-co2e).
* TR: Sum of execution time.
* EL: We will assume a 4 day lifespan or 24 hrs.
* RR: 12 vCPUs was used
* TR: 12 vCPUs was in the PC

# Execution

```{r calculate carbon intensity}
run_table_path = '../experiments/runner/experiments/new_runner_experiment/run_table.csv'

```

```{r Install Packages}
```

```{r setup}
cat("Loading Data:","\n")
data <- read.csv(run_table_path)
```

```{r energy}
# energy = average energy usage * 1 hour / 1000
# Calculate the energy consumption in kWh
data$energy_consumption <- (data$energy_usage * data$execution_time)
energy <- sum(data$energy_consumption) / 3600000
print(energy)
```
```{r}
# 268 grams of CO₂ equivalents per kilowatt-hour
carbon_intensity <- 268
```

```{r}
te <- 394
tir <- sum(data$execution_time) / 3600
el <- 35040
rr <- 12
tor <- 12
m_carbon <- 394 * (tir / el) * (rr / tor)
print(tir)
print(m_carbon)
```
```{r}
sci <- (energy + carbon_intensity) + m_carbon
print(sci)
```